### 2020-06-04 final/figures/net/fig.tex
Kinda wraping the presi

\begin{document}
\tikzset{
  cascaded/.style = {
    general shadow = {
      shadow scale = 1,
      shadow xshift = -1ex,
      shadow yshift = 1ex,
      draw,
      thick,
      fill = white},
    fill = white, 
    draw,
    thick,
    minimum width = 2.5cm,
    minimum height = 1.3cm},
  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
  squarednode/.style={rectangle, draw=red!60, fill=red!2, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
}
\begin{tikzpicture}

@@

  \node[squarednode] (pressure_i) at (0, -2.3) {Pressure};
  \node[squarednode] (pressure_o) at (8, -2.3) {Pressure};

@@

  \draw  [dashed] (-1.5,-1.2) rectangle (9.5,-3.4);

@@

\end{tikzpicture}

>>>>

\begin{document}
\tikzset{
  cascaded/.style = {
    general shadow = {
      shadow scale = 1,
      shadow xshift = -1ex,
      shadow yshift = 1ex,
      draw,
      thick,
      fill = white},
    fill = white, 
    draw,
    thick,
    minimum width = 2.5cm,
    minimum height = 1.3cm},
  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
  squarednode/.style={rectangle, draw, thick, minimum width = 2.5cm, minimum height = 1.3cm},
}
\resizebox{\columnwidth}{!}{%
  \begin{tikzpicture}

@@

  \node[squarednode] (pressure_i) at (-0.1, -2.3) {Pressure};
  \node[squarednode] (pressure_o) at (8, -2.3) {Pressure};

@@

@@

  \node[draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm] at (-0.2, 1.3) (params_1) {\shortstack{Simulation\\Parameters}};

\end{tikzpicture}}
